Subset occurrence data to IUCN Tropical Andes Lowland and Montane Forest

### 2023-08-02 code/L1/L1_TropicalAndes_subset_occ_forest.Rmd
add code to rasterize data

# Set file paths
```{r}
data_path<-file.path('G:/Shared drives/SpaCE_Lab_FRUGIVORIA/data/plants/L1')
output_path<- file.path('G:/Shared drives/SpaCE_Lab_FRUGIVORIA/data/plants/L1')
```

@@

# Read in data
```{r}
TropicalAndes_IUCNHabitat_Forest <- raster(file.path(data_path, "TropicalAndes_IUCNHabitat_Forest.tif"))
TropicalAndes_plant_occ <- read.csv(file.path(data_path,"TropicalAndes_GBIF_plant_occ_cleaned.csv"))
TropicalAndes_frugivore_occ <- read.csv(file.path(data_path,"TropicalAndes_GBIF_frugivore_occ_cleaned.csv"))
```

@@

# Rasterize occurrence data
```{r}

```

# Crop occurrence data to forest extent
```{r}

```

# Extract species list for plants and frugivore
```{r}
TropicalAndes_plant_SpeciesList <- unique(TropicalAndes_BIEN_traits$species)
TropicalAndes_frugivore_SpeciesList <- unique(TropicalAndes_BIEN_traits$species)
```

# Write data to csv
```{r}
write.csv(TropicalAndes_BIEN_traits, file = file.path(output_path,"TropicalAndes_BIEN_plant_traits.csv"))
write.csv(TropicalAndes_BIEN_traits, file = file.path(output_path,"TropicalAndes_BIEN_plant_traits.csv"))
write.csv(TropicalAndes_BIEN_traits, file = file.path(output_path,"TropicalAndes_BIEN_plant_traits.csv"))
write.csv(TropicalAndes_BIEN_traits, file = file.path(output_path,"TropicalAndes_BIEN_plant_traits.csv"))
```

>>>>

# Set file paths
```{r}
data_path<-file.path('G:/Shared drives/SpaCE_Lab_FRUGIVORIA/data/plants/L1')
data_path2<-file.path('G:/Shared drives/SpaCE_Lab_FRUGIVORIA/data/plants/L0')
output_path<- file.path('G:/Shared drives/SpaCE_Lab_FRUGIVORIA/data/plants/L1')
```

@@

# Read in data
```{r}
TropicalAndes_IUCNHabitat_Forest <- raster(file.path(data_path2, "TropicalAndes_IUCNHabitat_Forest.tif"))
#TropicalAndes_plant_occ <- read.csv(file.path(data_path,"TropicalAndes_GBIF_plant_occ_cleaned.csv"))
TropicalAndes_frugivore_occ <- read.csv(file.path(data_path,"TropicalAndes_GBIF_frugivore_occ_cleaned.csv"))
```

@@

```{r}
TropicalAndes_IUCNHabitat_Forest0.5 <- aggregate(TropicalAndes_IUCNHabitat_Forest, 50, fun=mean, na.rm=TRUE)
TropicalAndes_IUCNHabitat_Forest0.5
```

# Rasterize occurrence data
```{r}
coordinates(TropicalAndes_GBIF_plant_occ_cleaned) <- ~ decimalLatitude + decimalLongitude
coordinates(TropicalAndes_frugivore_occ) <- ~ decimalLatitude + decimalLongitude
# coerce to SpatialPixelsDataFrame
gridded(TropicalAndes_GBIF_plant_occ_cleaned) <- TRUE
gridded(TropicalAndes_frugivore_occ) <- TRUE
# coerce to raster
plant.raster <- raster(TropicalAndes_GBIF_plant_occ_cleaned)
frugivore.raster <- raster(TropicalAndes_frugivore_occ)
```

# Crop occurrence data to forest extent
```{r}
plant_crop <- crop(plants.raster, TropicalAndes_IUCNHabitat_Forest)
plant_occ_forest <- mask(plant_crop, TropicalAndes_IUCNHabitat_Forest)
plot(plant_occ_forest)
plant_occ_forest
```

```{r}
frugivore_crop <- crop(frugivores.raster, TropicalAndes_IUCNHabitat_Forest)
frugivore_occ_forest <- mask(frugivore_crop, TropicalAndes_IUCNHabitat_Forest)
plot(frugivore_occ_forest)
frugivore_occ_forest
```

# Extract species list for plants and frugivore
```{r}
TropicalAndes_plant_Forest_SpeciesList <- unique(TropicalAndes_BIEN_traits$species)
TropicalAndes_frugivore_Forest_SpeciesList <- unique(TropicalAndes_BIEN_traits$species)
```

# Write data to csv
```{r}
# subset plant occ, subset frugivore occ, plant species list, frugivore species list
write.csv(TropicalAndes_BIEN_traits, file = file.path(output_path,"TropicalAndes_BIEN_plant_traits.csv"))
write.csv(TropicalAndes_BIEN_traits, file = file.path(output_path,"TropicalAndes_BIEN_plant_traits.csv"))
write.csv(TropicalAndes_plant_SpeciesList, file = file.path(output_path,"TropicalAndes_plant_Forest_SpeciesList.csv"))
write.csv(TropicalAndes_frugivore_Forest_SpeciesList, file = file.path(output_path,"TropicalAndes_frugivore_Forest_SpeciesList"))
```
